Estimating carrying capacity for juvenile salmon using quantile random forest models

### 2025-02-20 analysis/paper/paper.Rmd
updated function to create partial dependence plots. Added script to create an example of a subset of PDPs for a capacity review paper.

# what packages are necessary
library(survey)
library(tidyverse)
library(QRFpaper)
library(janitor)
library(knitr)
library(pander)
library(magrittr)
library(sf)
library(english)
library(kableExtra)
library(ggpubr)

>>>>

# what packages are necessary
library(survey)
library(tidyverse)
# library(QRFpaper)
devtools::load_all()
library(janitor)
library(knitr)
library(pander)
library(magrittr)
library(sf)
library(english)
library(kableExtra)
library(ggpubr)
